\documentclass[sigconf]{acmart}

\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{listings}
\usepackage{xcolor}

\usepackage{bytefield}
\usepackage{paralist}
\usepackage[htt]{hyphenat}
\usepackage{xspace}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
\hypersetup{draft}

% Copyright
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference info
\acmYear{2021}
\copyrightyear{2021}
\setcopyright{acmcopyright}
\acmConference{CoNEXT '21}{December 7--10, 2021}{Virtual Event, Germany}
\acmPrice{TBA} % Use the data from your email from ACM rights management
\acmDOI{TBA} % Use the data from your email from ACM rights management
\acmISBN{TBA} % Use the data from your email from ACM rights management


\newcommand{\tcpls}{\texttt{TCPLS}\xspace}
\newcommand{\hello}{\tcpls \textsc{Hello}\xspace}
\newcommand{\join}{\tcpls \textsc{Join}\xspace}
\newcommand{\syn}{\texttt{SYN}\xspace}
\newcommand{\ack}{\texttt{ACK}\xspace}
\newcommand{\fin}{\texttt{FIN}\xspace}
\newcommand{\rst}{\texttt{RST}\xspace}

\newcommand{\synack}{\texttt{SYN+ACK}\xspace}

\newcommand{\tcp}{\texttt{TCP}\xspace}
\newcommand{\ssl}{\texttt{SSL}\xspace}
\newcommand{\mptcp}{\texttt{MPTCP}\xspace}
\newcommand{\udp}{\texttt{UDP}\xspace}
\newcommand{\dccp}{\texttt{DCCP}\xspace}
\newcommand{\sctp}{\texttt{SCTP}\xspace}
\newcommand{\xtp}{\texttt{XTP}\xspace}
\newcommand{\tls}{\texttt{TLS}\xspace}
\newcommand{\quic}{\texttt{QUIC}\xspace}
\newcommand{\tcpcrypt}{\texttt{tcp\-crypt}\xspace}

\newcommand{\mvfst}{\texttt{mvfst}\xspace}
\newcommand{\msquic}{\texttt{msquic}\xspace}
\newcommand{\quicly}{\texttt{quicly}\xspace}

\newcommand{\todo}[1]{\textcolor{red}{\textbf{[TODO: #1]}}}
%\newcommand{\todo}[1]{}
\newcommand{\fr}[1]{\textcolor{blue}{\textbf{FR: #1}}}
\hyphenation{Client-Hello Cli-entHello ClientHel-lo}

\begin{document}

\title{TCPLS: Modern Transport Services with TCP and TLS}
%\titlenote{Produces the permission block, and copyright information}
%\subtitle{Extended Abstract}

\author{Florentin Rochet}
\affiliation{%
   \institution{University of Edinburgh}
   \country{Scotland}
}
\email{frochet@ed.ac.uk}

\author{Emery Assogba}
\affiliation{%
	\institution{UCLouvain}
	\country{Belgium}
}
\email{emery.assogba@uclouvain.be}

\author{Maxime Piraux}
\affiliation{%
	\institution{UCLouvain}
	\country{Belgium}
}
\email{maxime.piraux@uclouvain.be}

\author{Korian Edeline}
\affiliation{%
	\institution{Universit\'e de Li\`ege}
	\country{Belgium}
}
\email{korian.edeline@gmail.com}

\author{Benoit Donnet}
\affiliation{%
	\institution{Universit\'e de Li\`ege}
	\country{Belgium}
}
\email{benoit.donnet@uliege.be}

\author{Olivier Bonaventure}
\affiliation{
  \institution{UCLouvain}
  \country{Belgium}
}
\email{olivier.bonaventure@uclouvain.be}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003033.10003039.10003048</concept_id>
<concept_desc>Networks~Transport protocols</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003033.10003039.10003040</concept_id>
<concept_desc>Networks~Network protocol design</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Networks~Transport protocols}
\ccsdesc[500]{Networks~Network protocol design}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{F. Rochet et al.}

\begin{abstract}
  \tcp and \tls are among the essential protocols in today's Internet. \tcp
  ensures reliable data delivery while \tls secures the data transfer.
  Although they are very often used together, they have been designed
  independently following the Internet layered model.  This paper  demonstrates the various benefits that a closer integration between \tcp and \tls would bring.

  By leveraging the extensible \tls 1.3 records, we combine \tcp and \tls into
  \tcpls to build modern transport services such as multiplexing, connection
  migration, stream steering, and bandwidth aggregation. These services do not
  modify the \tcp wire format and are resistant to middleboxes. \tcpls offers a
  powerful API enabling applications to precisely express the required
  transport services, ranging from a single-path single-stream connection to a
  multi-stream connection over several network paths, enabling choices between
  aggregated bandwidth and Head-of-Line blocking avoidance.

%(mp): L'abstract revient un peu en arrière par rapport au schéma du papier,
%j'ai proposé une version qui suit mieux la trame actuelle.
%  We propose \tcpls, a modern and secure transport that is wire-compatible with
%  \tcp and transparent for middleboxes. It suggests a new approach for \tcp
%  extensibility and leverages \tls 1.3 to support modern services such as
%  connection migration, seamless handovers, and bandwidth aggregation. To
%expose
%  the new capabilities, we build a new API and research a method to express
%  novel transport services. We desgined a Stream Steering mechanic to let the
%  application steers and combines features offered by the protocol, easily
%  managing the session from a single-path stream connection to features similar
%  to \mptcp's bandwidth aggregation or \quic's Head-of-Line blocking
%resilience.
%  The Stream Steering mechanic exposed to the applications allows it to easily
%  program complex transport mechanisms with interesting properties, such as a
%  new transport capability called the Application-level Connection Migration
%  having different properties than the passive connection migration, and
%  more adapted for several connection migration scenarios.

  Compared to \mptcp, our \tcpls prototype offers more control to the
  application and can be easily deployed as an extension to user-space \tls
  libraries,  while being implemented at a low cost. Measurements demonstrate
  that it offers higher performance than existing \quic libraries with a super
  set of transport services.
\end{abstract}

\maketitle

\input{body}

\balance
\bibliographystyle{ACM-Reference-Format}
\bibliography{reference}
\newpage
\appendix
\label{sec:appendices}
\input{appendix}

\end{document}
